---
title: "Lists - In Class Exercises"
author: "Dr. Shoemaker"
date: "DATA 2401"
output: html_document

---

# Exercises: 

Make a list that contains the information on a single playing card. Suit, face, and value. 

```{r}
Card <- list(
  Suit = ("Heart"),
  Face = ("Queen"),
  Value = 12
)

```


Make a second list where each element contains all the options for suit, face, and value, respectively. 

```{r}
cards <- list(
  face = c("ace", "king", "queen", "jack"),
  suit = c("diamond", "clover", "heart", "spade"),
  values = c(1,13,12,11)
)


```


If `Newlist <- list(a=1:10, b="Good morning", c="Hi")`, write an R statement that will add 1 to each element of the first vector in Newlist.

```{r}
Newlist <- list(a=1:10, b="Good morning", c="Hi")

Newlist[[1]] + 1 
```

If `b <- list(a=1:10, c="Hello", d="AA")`, write an R expression that will give all elements of the first vector of b, except the second, and write another that returns only elements of `a` that are greater than 7.

```{r}
b <- list(a=1:10, c="Hello", d="AA")
tag_variable <- "a"
b[[tag_variable]]

b$a
b$a > 7
b$a [b$a > 7]  # brackets for indexing

b$a [-2]
b[[1]][-2]

b[-2] # gets rid of the 2nd list 
```

Let `x <- list(a=5:10, c="Hello", d="AA")`, write an R statement to add a new item z = "NewItem" to the list x.

```{r}
x <- list(a=5:10, c="Hello", d="AA")
 x$z <- "NewItem"

```
